Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation

### 2020-09-22 Article/ici_submm_cloudcorr.tex
small changes in Sec 3

\subsection{QRNN network structure}
%
\begin{figure*}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-single applied to I2V.}
	\label{fig:grid_search}	
\end{figure*}
In this study, we investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size. The optimization of other hyper-parameters was not performed and were chosen empirically. Firstly, we performed a grid search to define the structure of the neural network. We evaluated the performance for three sizes of hiddden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512]. The mean quantile loss and CRPS over all predicted quantiles was computed for each configuration (Fig.~\ref{fig:grid_search}). Increasing the complexity of the network by increasing the layer width and depth has a positive impact on performance. However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance. On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected. For optimising the training parameters, a customised  learning rate scheduler was implemented. The initial learning rate was reset after a certain number of epochs.  We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs. The best neural network performance was obtained when the network was trained three times with a new initial learning rate. For each training, if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2. 
In order to select the batch size, we simply compared the performance for for two batch sizes: 128 and 256, and the former gave better results. Concerning number of epochs, we obtained best results when the network was trained longer. Choosing a lower value of epochs (e.g. 50), did not affect the accuracy of the median value, yet deteriorated the prediction uncertainty. We did not optimise the type of activation function and Rectified Linear Unit (ReLu) was used in all layers.

Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other channnels and other QRNN models as well. All the results described in this study used an identical hyper-parameter configuration.

@@

In this section, we use the point estimates to formulate a cloud filtering scheme. All cases with  cloud correction greater than a certain threshold are classified as cloudy and omitted from the dataset. Cloud correction is calculated as the difference of the point estimate and the corresponding measurement. Since this is a pure-filter, for the cases classified as clear-sky, the a priori values are used instead of the point estimates.

To implement the cloud filtering scheme, we chose 5\,K cloud correction as the filtering threshold. All cases with correction greater than 5\,K were rejected. In order to analyse the performance of the filtering threshold, the deviations of the filtered measurements to the simulated NFCS values were calculated. Fig.~\ref{fig:error_distributions} shows the distribution of the deviations for filtered(red) and original datasets(green). Cloud contamination causes a reduction in the brightness temperatures, and introduces a large negative bias in the error distributions. Without any cloud impact, the error distributions must follow a Gaussian distribution with a narrow spread. When filtering is activated, and all cases with correction greater than 5\,K are rejected, the resulting distributions have a low but asymmetric spread. The right side of the distributions follows measurement noise, as expected, and the left side has a significantly smaller negative skewness than the measurements. This indicates that 5\,K filter can successfully remove cases associated with high cloud impact. However at the same time, the asymmetric error distribution indicates that cases with low cloud impact are erroneously classified as clear-sky.

For a quantitative assessment of the performance achieved with cloud filtering, we calculated the average error bias, MAE (mean absolute error) and standard deviation of the errors. The asymmetry of error distributions around their mean is also calculated through the measure of skewness. Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness: 
\begin{equation}
g_1 = \frac{m_3}{m_2^{3/2}}, 
\end{equation}
where $m_2$ and $m_3$ are biased sample's second and third central moments. The error metrics corresponding to the error distributions described in Fig.~\ref{fig:error_distributions} are provided in Table~\ref{tab:error_statistics_ici} under label "Filtered(5\,K)". The average bias in I1V measurements is -1.88\,K, and rejecting around 6\% of the cases as cloudy reduces the bias to -0.32\,K. The standard deviation also reduces to 1.07\,K from 8.84\,K. Similarly for I2V, the average error bias in all sky measurements is -1.04\,K, that reduces to -0.24\,K after filtering. The corresponding improvement in MAE was almost 65\%. Only 3.7\% of the total cases were rejected to achieve this accuracy. For I3V, filtering classifies 2.3\% of the total cases as cloudy and reduces the bias to 0.18\,K from -0.63\,K and the standard deviation from 5.95\,K to 0.91\,K. The results from QRNN-all are also shown in the same table. Using all 183\,GHz channels concurrently has no notable impact on the cloud filtering. Almost similar statistics are obtained from QRNN-single and QRNN-all. Overall for all three channels, the notable decrease in the errors indicates that the cloud filter is effective in removing most of the cloudy cases, however few cases with low cloud impact still pass through the filter and deteriorate the performance. This indicates that though a pure-filtering approach can prove as a reliable procedure for removing cases with high cloud impact, additional measures are needed to remove cases with low cloud impact.

A lower filtering threshold can help alleviate this problem to certain extent, however that can come at the cost of high rejection rate. We investigated the performance of cloud filtering with different threshold values. Fig.~\ref{fig:filtering_thresholds} shows the average errors obtained from different filtering thresholds and the corresponding percentage of data omitted. Lowering the filtering threshold from 5\,K to 2.5\,K has only a small effect on the filter performance. However, a further decrease in the filtering threshold decreases the average error bias significantly, albeit with a high rejection rate. For example, for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the mean error bias of the subset is -0.06\,K, MAE is 0.59\,K and the standard deviation is 0.75\,K. Though, these values are comparable to the NFCS simulations, the high performance comes at the cost of rejecting more than 30\% of the total cases. The high fraction of rejection is a consequence of clear-sky cases being erroneously classified as cloudy. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy.

\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
	\caption{A comparison of the  average bias when pure-filtering approach (QRNN-single) is applied with different thresholds (red curves). The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).}
	\label{fig:filtering_thresholds}	
\end{figure}

@@

The QRNN prediction accuracy is estimated by computing the deviation of the best estimate to its corresponding NFCS value (Fig.~\ref{fig:error_distributions}). The predicted values have a symmetric distributions albeit with a large spread. The large spread on the left is due to cases which end up with incomplete cloud correction, while spread on the right is from cases where the predicted values are warmer than the simulations. For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact. If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduces a negative bias.

For a quantitative assessment of the errors, we calculated the error metrics described in Sect.~\ref{sec:cloud_filtering} and the results are displayed in Table~\ref{tab:error_statistics_ici}. The average bias in I1V measurements is -1.88\,K, which reduces to -0.06\,K after cloud correction. The corresponding standard deviation is 0.98\,K in comparison to 8.84\,K in the measurements. The prediction accuracy of QRNN is further higher when filtering is made on the predictions. In this case, the residual bias is only -0.04\,K, and the standard deviation is 0.73\,K, which is in fact of the order of measurement noise (0.80\,K). Similar results are seen for I2V, though a better performance of QRNN is observed. In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction. The MAE reduces from 1.52\,K to 0.52\,K. Removing cases with correction greater than 5\,K from the predictions removes 3.7\% of the data and reduces the absolute error to 0.46\,K and the bias to 0\,K. The standard deviation of the resulting dataset is only 0.59\,K as compared to 0.80\,K from noise. The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of the predicted distributions is sharper. In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact. In the predicted dataset, the bias is 0.01\,K and the MAE is 0.51\,K in comparison to 1.15\,K  in the measurements. Including correction along with filtering reduces the MAE further down to 0.47\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).

Next, we describe the results from QRNN-all. In this model, all 183\,GHz channels along with other sub-mm channels are included while training. This model is designed to identify if other channels of the same frequency can provide auxiliary information in the training process. The results from QRNN-all all are provided in the last columns of Table~\ref{tab:error_statistics_ici}. For I1V, using additional information from other two 183\,GHz channels has only a slight positive impact on the predictions. In the prediction dataset, the average bias for QRNN-all and QRNN-single is identical, but the MAE in QRNN-all are almost 4.5\% less than QRNN-single. However when the predictions are filtered with 5\,K threshold, the performance of both models is quite similar. This indicates that information from other channels only assists in slightly improving the correctness of cases associated with high cloud impact in I1V. The predictions of cases with low cloud impact have no significant gain. For I2V, the predictions from QRNN-all have a slightly worse average error bias than QRNN-single, yet a significant improvement in the prediction accuracy is observed. When all predictions are considered, the MAE is 0.44\,K in comparison to 0.52\,K from QRNN-single, showing an improvement of almost 15\%. Similarly the standard deviation of the errors is only 0.67\,K, which is notably smaller than the measurement noise. Additionally, when the predicted dataset is filtered with 5\,K threshold, the accuracy is even better. The mean absolute bias reduces to 0.39\,K and standard deviation to 0.50\,K. This implies that cases pertaining to clear-sky conditions and relatively low/no cloud impact benefit the most from the auxiliary information. This is in contrast to I1V, where accuracy of such cases remained unaffected. For I3V, the performance of QRNN-all is comparable to that for I2V. For I3V, the MAE in QRNN-all is 0.46\,K compared to 0.51\,K from QRNN-single, and the corresponding standard deviations are 0.68\,K and 0.77\,K. Removing the cases with cloud impact greater than 5\,K from the predictions, leads to no change in the average bias, but the MAE and standard deviation reduce by almost  8\% and 20\% respectively. This is again a consequence of improved prediction accuracy of cases with low/no cloud impact.

In order to quantify the positive effect of QRNN-all on cases with high cloud impact, the error statistics for all cases with cloud correction greater than 10\,K were computed (Table~\ref{tab:error_statistics_ici_high_cloud_impact}). For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but very high prediction errors. QRNN-all improves the overall error bias from -0.53\,K to -0.38\,K and the standard deviation from 3.13\% to 2.63\%, but is unsuccessful in removing the cloud impact completely. A likewise improvement is also observed for I2V. Despite both models being only partially successful in removing the cloud impact, QRNN-all has a better performance among the two. For I2V, such cases form only 2.25\% of the testing dataset. Predictions from QRNN-all have slightly worse values for average error bias, but both MAE and standard deviation improve by over 20\%. For I3V also, the cases with high cloud impact, though very low in number, also gained positively from the auxiliary information.

The results show that both QRNN-single and QRNN-all are successful in predicting NFCS values for I2V, and I2V, and partially successful for I1V. The resulting error distributions are symmetric with low bias and standard deviation. For I2V and I3V, the variability of errors is even smaller than the noise. This is a consequence of predictions for cases associated with clear sky conditions. QRNN predictions are weighted mean of measurements between channels. For clear-sky conditions, the averaging of cases observed by multiple channels can cancel out the noise. The cancelling of noise is stronger in QRNN-all as all 183\,GHz channels are used concurrently. The lower prediction accuracy of I1V can be explained by the fact that it is the outermost 183\,GHz channel and the other sub-mm channels cannot provide a full coverage for the hydrometeor impact in I1V. Depending upon the atmospheric scenarios, there is always a portion of data detected by I1V, but never seen by any other channel. Though such cases are few, QRNN cannot learn to predict the clear-sky values accurately for cases which lie outside the coverage area. Besides this, lower representation of high cloud impact cases in the training set also affects QRNN accuracy.

@@

Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuarcy) to predicted errors. The predicted dataset is constructed by drawing random samples from the posteriori distribution. We do derive any sample from outside $\pm3\sigma$. The predicted error is deviation of random sample to its median. For QRNN-single, the predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically. For QRNN-all, the predicted and observed errors have a better agreement and their spread is symmetric. The results show that both QRNN-single and QRNN-all is not able to represent the left wings of the distribution. This could also be a sampling issue, as the high errors we try to predict form a very small fraction of the complete dataset.

For further analysis, we compared the distribution of predictions from QRNN with the a priori distribution. In a model with high performance, the posterior distribution of the predictions should be similar to the a priori distribution of training dataset. A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of the true value in different prediction intervals. This is also commonly known as calibration plot. Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals on the test dataset for I1V. For both QRNN models, the predictions for the complete test dataset are well calibrated and follow the y=x line. This shows that the training and test datasets come from the same a priori distribution. On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, for both models, the predictions in all the intervals are poorly calibrated. In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated. In the test and training datasets, the clear-sky cases and cases with low cloud impact dominate the a priori distribution. The a priori distribution of cloudy cases is significantly different to the clear-sky cases, thus leading to poorly calibrated predictions for former. We also plotted the calibration curves for I2V and I3V (figure not shown). For both these channels, predictions over complete dataset were well calibrated for both QRNN-single and QRNN-all, but for subset with threshold 10\,K, the slightly poor calibrations were observed in QRNN-single. This is in contrast with I1V, where both models had poor calibrations for cases with high cloud impact.

Lastly, we investigated that if the uncertainty estimates given by QRNN are representative of prediction errors.  We divided the 94\% confidence interval ($\pm2\sigma$ ) into three bins and estimated the prediction error distribution for each (Fig.~\ref{fig:error_distribution_uncertainty_bins}). Similar results were also obtained for QRNN-all (figure not shown). For all three channels, an increase in the prediction errors with uncertainty is observed. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship. This suggests that QRNN can reliably represent the quality of predictions through their uncertainty estimates.

These three different types of analysis show that both QRNN-single and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact. This is not unexpected, as such cases form a small subset of the training set and their priori distribution could be different from the entire dataset. Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately. A larger training dataset would be required to increase the representation of such cases in QRNN.

>>>>

\subsection{QRNN network structure}
%
\begin{figure*}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-single applied to I2V.}
	\label{fig:grid_search}	
\end{figure*}
In this study, we investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size. The optimization of other hyper-parameters was not performed and were chosen empirically. Firstly, we performed a grid search to define the structure of the neural network. We evaluated the performance for three sizes of hiddden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512]. The mean quantile loss and CRPS over all predicted quantiles was computed for each configuration (Fig.~\ref{fig:grid_search}). Increasing the complexity of the network by increasing the layer width and depth has a positive impact on performance. However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance. On basis of these results, a neural network with four hidden layers and 128 neurons in each layer is selected. For optimising the training parameters, a customised  learning rate scheduler was implemented. The initial learning rate was reset after a certain number of epochs.  We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs. The best neural network performance was obtained when the network was trained three times. Each time with a new initial learning rate. For each training, if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2. 
In order to select the batch size, we simply compared the performance for two batch sizes: 128 and 256, and the former gave better results. Concerning number of epochs, we obtained best results when the network was trained longer. Choosing a lower value of epochs (e.g. 50), did not affect the accuracy of the median value, yet deteriorated the prediction uncertainty. We did not optimise the type of activation function and Rectified Linear Unit (ReLu) was used in all layers.

Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other QRNN models and their multiple configurations. All the results described in this study use an identical hyper-parameter configuration.

@@

In this section, we use the point estimates to formulate a cloud filtering scheme. All cases with  cloud correction greater than a certain threshold are classified as cloudy and omitted from the dataset. Cloud correction is calculated as the difference of the point estimate to the corresponding measurement. Since this is a pure-filter, for the cases classified as clear-sky, the a priori values are used instead of the point estimates.

To implement the cloud filtering scheme, we chose 5\,K cloud correction as the filtering threshold. All cases with correction greater than 5\,K were rejected. In order to analyse the performance of the filtering threshold, the deviations of the filtered measurements to the NFCS simulations were calculated. Fig.~\ref{fig:error_distributions} shows the distribution of the deviations for filtered(red) and original datasets(green). Cloud contamination causes a reduction in the brightness temperatures, and introduces a large negative bias in the error distributions. Without any cloud impact, the error distributions must follow a Gaussian distribution with a narrow spread. When filtering is activated, the resulting distributions have a low but asymmetric spread. The right side of the distributions follows the measurement noise, as expected. The left side has a significantly smaller negative skewness than the measurements. This indicates that 5\,K filter can successfully remove cases associated with high cloud impact. However at the same time, the asymmetric error distribution indicates that cases with low cloud impact are erroneously classified as clear-sky.

For a quantitative assessment of the performance achieved with cloud filtering, we calculated the average error bias, MAE (mean absolute error) and standard deviation of the errors. The asymmetry of error distributions around their mean is also calculated through the measure of skewness. Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness: 
\begin{equation}
g_1 = \frac{m_3}{m_2^{3/2}}, 
\end{equation}
where $m_2$ and $m_3$ are biased sample's second and third central moments. The error metrics corresponding to the error distributions described in Fig.~\ref{fig:error_distributions} are provided in Table~\ref{tab:error_statistics_ici} under label "Filtered(5\,K)". The average bias in I1V measurements is -1.88\,K, and rejecting around 6\% of the cases as cloudy reduces the bias to -0.32\,K. The standard deviation also reduces to 1.07\,K from 8.84\,K. Similarly for I2V, the average error bias in all sky measurements is -1.04\,K, that reduces to -0.24\,K after filtering. The corresponding improvement in MAE is almost 65\%. Only 3.7\% of the total cases are rejected to achieve this accuracy. For I3V, filtering classifies 2.3\% of the total cases as cloudy and reduces the bias to 0.18\,K from -0.63\,K and the standard deviation from 5.95\,K to 0.91\,K. The results from QRNN-all are also shown in the same table. Using all 183\,GHz channels concurrently has no notable impact on the cloud filtering. Almost similar statistics are obtained from QRNN-single and QRNN-all. Overall for all three channels, the notable decrease in the errors indicates that the cloud filter is effective in removing most of the cloudy cases, however few cases with low cloud impact still pass through the filter and deteriorate the performance. Thus pure-filtering approach can prove as a reliable procedure for removing cases with high cloud impact, but additional measures are needed to remove cases with low cloud impact.

A lower filtering threshold can help alleviate this problem to certain extent, however that can come at the cost of high rejection rate. We investigated the performance of cloud filtering with different threshold values. Fig.~\ref{fig:filtering_thresholds} shows the average errors obtained from different filtering thresholds and the corresponding percentage of data omitted. Lowering the filtering threshold from 5\,K to 2.5\,K has only a small effect on the filter performance. However, a further decrease in the filtering threshold decreases the average error bias significantly, albeit with a high rejection rate. For example for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the mean error bias of the subset is -0.06\,K, MAE is 0.59\,K and the standard deviation is 0.75\,K. Though, these values are comparable to the NFCS simulations, the high performance comes at the cost of rejecting more than 30\% of the total cases. The high fraction of rejection is a consequence of clear-sky cases being erroneously classified as cloudy. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy.

\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
	\caption{A comparison of the  average bias when pure-filtering approach is applied with different thresholds (red curves). The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves). The results are from QRNN-single. }
	\label{fig:filtering_thresholds}	
\end{figure}

@@

The QRNN prediction accuracy is estimated by computing the deviation of the best estimate to its corresponding NFCS simulation(Fig.~\ref{fig:error_distributions}). The predicted values have symmetric error distributions albeit with a large spread. The large spread on the left is due to cases which end up with incomplete cloud correction, while the spread on the right is from cases where the predicted values are warmer than the simulations. For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact. If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduces a negative bias.

For a quantitative assessment of the errors, we calculated the error metrics described in Sect.~\ref{sec:cloud_filtering} and the results are displayed in Table~\ref{tab:error_statistics_ici}. The average bias in I1V measurements is -1.88\,K, which reduces to -0.06\,K after cloud correction. The corresponding standard deviation is 0.98\,K in comparison to 8.84\,K in the measurements. The prediction accuracy of QRNN-single is further higher when filtering is made on the predictions. In this case, the residual bias is only -0.04\,K, and the standard deviation is 0.73\,K, which is in fact of the order of measurement noise (0.80\,K). Similar results are seen for I2V, though a better performance is observed. In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction. The MAE reduces from 1.52\,K to 0.52\,K. Removing cases with correction greater than 5\,K from the predictions removes 3.7\% of the data and reduces the absolute error to 0.46\,K. The standard deviation of the resulting dataset is only 0.59\,K as compared to 0.80\,K from noise. The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of distributions is sharper. In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact. In the predicted dataset, the bias is 0.01\,K and the MAE is 0.51\,K. Including correction along with filtering reduces the MAE further down to 0.47\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).

Next, we describe the results from QRNN-all. In this model, all 183\,GHz channels along with other sub-mm channels are included while training. This model is designed to identify if other channels of the same frequency can provide auxiliary information in the training process. The results from QRNN-all all are provided in the last columns of Table~\ref{tab:error_statistics_ici}. For I1V, using additional information from other two 183\,GHz channels has only a slight positive impact on the predictions. In the prediction dataset, the average bias for QRNN-all and QRNN-single is identical, but the MAE in QRNN-all are almost 4.5\% less than QRNN-single. However when the predictions are filtered with 5\,K threshold, the performance of both models is quite similar. This indicates that information from other channels is only slightly helpful in improving the correctness of cases associated with high cloud impact. The predictions for cases with low cloud impact have no significant gain. For I2V, the predictions from QRNN-all have a slightly worse average error bias than QRNN-single, yet a significant improvement in the prediction accuracy is observed. When all predictions are considered, the MAE is 0.44\,K in comparison to 0.52\,K from QRNN-single, showing an improvement of almost 15\%. Similarly the standard deviation of the errors is only 0.67\,K, which is notably smaller than the measurement noise. Additionally, when the predicted dataset is filtered with 5\,K threshold, the accuracy is even better. The MAE reduces to 0.39\,K and standard deviation to 0.50\,K. This implies that cases pertaining to clear-sky conditions and relatively low/no cloud impact benefit the most from the auxiliary information. This is in contrast to I1V, where accuracy of such cases remained unaffected. For I3V, the performance of QRNN-all is comparable to that for I2V. For I3V, the MAE in QRNN-all is 0.46\,K compared to 0.51\,K from QRNN-single, and the corresponding standard deviations are 0.68\,K and 0.77\,K. Removing the cases with cloud impact greater than 5\,K from the predictions, leads to no change in the average bias, but the MAE and standard deviation reduce by almost  8\% and 20\% respectively. This is again a consequence of improved prediction accuracy of cases with low/no cloud impact.

In order to quantify the positive effect of QRNN-all on cases with high cloud impact, the error statistics for all cases with cloud correction greater than 10\,K were computed (Table~\ref{tab:error_statistics_ici_high_cloud_impact}). For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but very low prediction accuracy. QRNN-all improves the overall error bias from -0.53\,K to -0.38\,K and the standard deviation from 3.13\% to 2.63\%, but is unsuccessful in removing the cloud impact completely. A likewise improvement is also observed for I2V. Despite both models being only partially successful in removing the cloud impact, QRNN-all has a better performance among the two. For I2V, such cases form only 2.25\% of the testing dataset. Predictions from QRNN-all have slightly worse values for average error bias, but both MAE and standard deviation improve by over 20\%. For I3V also, the cases with high cloud impact, though very low in number, also gain positively from the auxiliary information.

The results show that both QRNN-single and QRNN-all are successful in predicting NFCS values for I2V, and I3V, and partially successful for I1V. The resulting error distributions are symmetric with low bias and standard deviation. For I2V and I3V, the variability of errors is even smaller than the noise. This is a consequence of predictions for cases associated with clear sky conditions. QRNN predictions are weighted mean of measurements between channels. For clear-sky conditions, the averaging of cases observed by multiple channels can cancel out the noise. The cancelling of noise is stronger in QRNN-all as all 183\,GHz channels are used concurrently. The lower prediction accuracy of I1V can be explained by the fact that it is the outermost 183\,GHz channel. The other sub-mm channels cannot provide a full coverage for the hydrometeor impact in I1V. Depending upon the atmospheric scenarios, there is always a portion of data detected by I1V, but never seen by any other channel. Though such cases are few, QRNN cannot learn to predict the clear-sky values accurately for cases which lie outside the coverage area. Besides this, lower representation of high cloud impact cases in the training set also affects QRNN accuracy.

@@

Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors. The predicted dataset is constructed by drawing random samples from the posteriori distribution. We do derive any sample from outside $\pm3\sigma$. The predicted error is deviation of random sample to its median. For QRNN-single, the predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically. For QRNN-all, the predicted and observed errors have a better agreement and the spread is symmetric for the former. The results show that both QRNN-single and QRNN-all are not able to represent the left wings of the distribution. This could also be a sampling issue, as the high errors we try to predict form a very small fraction of the complete dataset.

For further analysis, we compared the distribution of predictions from QRNN with the a priori distribution. In a  high performing QRNN model, the posteriori distribution of the predictions should be similar to the a priori distribution of training dataset. A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of the true value in different prediction intervals. This is also commonly known as calibration plot. Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals on the test dataset for I1V. For both QRNN models, the predictions for the complete test dataset are well calibrated and follow the y=x line. This shows that the training and test datasets come from the same a priori distribution. On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, for both models, the predictions in all the intervals are poorly calibrated. In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated. The clear-sky cases dominate the test/training dataset, thus the a priori distribution is representative of the same. The a priori distribution of cloudy cases is different to the clear-sky cases, therefore the predictions are poorly calibrated for the former. We also plotted the calibration curves for I2V and I3V (figure not shown). For both these channels, predictions over complete dataset were well calibrated for both QRNN-single and QRNN-all, but for subset with threshold 10\,K, slightly poor calibrations were observed in QRNN-single. This is in contrast with I1V, where both models had poor calibrations for cases with high cloud impact.

Lastly, we investigated that if the uncertainty estimates given by QRNN are representative of prediction accuracy. Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the errors of best estimate binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval. Similar results were also obtained for QRNN-all (figure not shown). For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship.

The results show that both QRNN-single and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact. This is not unexpected as such cases form a small subset of the training set and their priori distribution is different from the entire dataset. Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately. A larger training dataset would be required to increase the representation of such cases in QRNN.
